\pagestyle{myFancy}
\chapter{Gauge Theories Simulations on Non-Hypercubic Lattice}

\section{Rotational Invariance Restoration}
The restoration of spacetime symmetries in the continuum limit is an important aspect of lattice field theory.
Minkowskian spacetime is invariant under the action of the Poincaré group, that includes translations, rotations in the $3$-dimensional space, and boosts.
When performing the Wick rotation, boosts become rotations in the planes formed by each one of the \emph{spacelike} axis and the euclidean time.
The euclidean spacetime is therefore invariant, in the continuum, under translations:
\begin{equation}
    x^\mu \to x^\mu + \varepsilon^\mu \label{3:TranslCont}
\end{equation}
and under rotations in $4$ dimensions:
\begin{equation}
    x^\mu \to R^\mu_\nu x^\nu \qquad\text{with}\qquad R\in\SO(4) \label{3:RotCont}
\end{equation}
These invariances do not hold true anymore if the spacetime is discretized: a generic lattice is, in fact, invariant only under translations of multiples of the lattice spacing $a$:
\begin{equation}
    x \to x + a\mu \qquad\text{with}\qquad x\in\Lambda \label{3:TraslDiscr}
\end{equation}
and under certain rotations:
\begin{equation}
    x \to \Gamma x \qquad\text{with}\qquad x\in\Lambda, \Gamma\in G_\Lambda \label{3:RotDiscr}
\end{equation}
where $G_\Lambda\subset\SO(4)$ is a discrete subset of the full rotational group $\SO(4)$ that depends on the lattice $\Lambda$.
For example, $\Lambda=\Lambda_{SH}$ is a SH lattice, then $G_{\Lambda_{SH}}$ is the $384$-elements group with all possible reflections on every coordinate plane and rotations of multiples of $90^\degree$ around each one of the $4$ axis.
The fact that the symmetries between the discrete and the continuum cases are different is not a problem itself, as long as when approaching the continuum limit the lattice symmetries tend to the continuum ones.
This is the case for the translational symmetry: if $a\to0$, \eqref{3:TraslDiscr} becomes \eqref{3:TranslCont}.
However, the rotational symmetry is not restored when the continuum limit is taken (\eqref{3:RotDiscr} does not become \eqref{3:RotCont} when $a\to0$), as the Simple Hypercubic lattice is invariant under rotations of multiples of $90^\degree$ independently from the value of the lattice spacing.
For this reason, studies on the restoration of rotational symmetry have been made, through the computation of rotational invariant quantities.
An example of these studies is the 1982 article of Lang and Rebbi~\cite{Lang:1982tj}, where the static quark potential $V(r)$, obtained from the correlator of two Polyakov loops (see \eqref{1:PolyakovPotential}), at different lattice spacings has been studied.

\section{Non-Hypercubic Lattice}
